---
params:
  Name: "LOUISIANA ICE PROCESSING" 
  Longitude: -91.56805267
  Latitude: 30.94074023
title: "`r params$Name`"
format:
  html:
    theme: flatly
    toc: true
    toc-location: left
    code-fold: true
    embed-resources: true
    page-layout: full
    includes:
      in-header: |
        <!-- Google tag (gtag.js) -->
        <script async src="https://www.googletagmanager.com/gtag/js?id=G-Y0JF41VY73"></script>
        <script>
          // Get the full path after the domain
          let pagePath = window.location.pathname;
          
          // Remove .html extension if present
          pagePath = pagePath.replace(/\.html$/, "");
          
          // Extract just the facility name from the path
          // e.g., "/facility/ADAMS_COUNTY_DET_CENTER" → "ADAMS_COUNTY_DET_CENTER"
          let facilityName = pagePath.split("/").pop();
        
          window.dataLayer = window.dataLayer || [];
          function gtag(){dataLayer.push(arguments);}
          gtag('js', new Date());
          gtag('config', 'G-Y0JF41VY73', {
            `page_path`: pagePath 
          });
          
          
          // Log a custom GA event for facility views
          gtag('event', 'view_facility', {
            facility_name: facilityName
          });
        </script>
    css: |
      body {
        font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
      }
      .header-section {
        background: linear-gradient(135deg, #2c3e50 0%, #34495e 100%);
        color: white;
        padding: 3rem 2rem;
        margin: -1rem -1rem 3rem -1rem;
        border-radius: 0 0 15px 15px;
        text-align: center;
        position: relative;
        overflow: visible;
        min-height: 200px;
      }
      .header-section h1 {
        font-size: 2.5rem;
        margin-bottom: 0.5rem;
        margin-top: 1rem;
      }
      .header-section h3 {
        font-size: 1.2rem;
        opacity: 0.9;
        margin-bottom: 0.5rem;
      }
      .header-section p {
        font-size: 1rem;
        opacity: 0.8;
      }
      .logo-top-right {
        display: none !important;
      }
      .stats-container {
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 3rem;
        margin: 3rem 0;
      }
      .chart-container {
        background: white;
        padding: 1.5rem;
        border-radius: 10px;
        box-shadow: 0 2px 10px rgba(0,0,0,0.1);
      }
      .insights-box {
        background: linear-gradient(135deg, #e8f4fd 0%, #f0f8ff 100%);
        border-left: 5px solid #3498db;
        padding: 2rem;
        border-radius: 8px;
        margin: 2rem 0;
      }
      .news-section {
        background-color: #f8f9fa;
        padding: 2rem;
        border-radius: 10px;
        margin-top: 3rem;
        border-left: 4px solid #28a745;
      }
      .facility-table {
        width: 100%;
        margin: 2rem auto;
        max-width: 800px;
      }
      .map-container {
        text-align: center;
        margin: 2rem 0;
        background: white;
        padding: 1.5rem;
        border-radius: 10px;
        box-shadow: 0 2px 10px rgba(0,0,0,0.1);
      }
      .map-container iframe {
        border: 0;
        border-radius: 10px;
        box-shadow: 0 2px 10px rgba(0,0,0,0.1);
        width: 100%;
        max-width: 800px;
      }
      .map-container p {
        margin-top: 1rem;
        font-style: italic;
        color: #666;
        text-align: center;
        font-size: 0.9em;
      }
      h2 {
        color: #2c3e50;
        border-bottom: 2px solid #3498db;
        padding-bottom: 0.5rem;
        margin-top: 3rem;
      }
      .section-spacing {
        margin: 3rem 0;
      }
      
      /* Sidebar styling for TOC */
      .sidebar {
        position: relative;
      }
      
      /* Button hover effects */
      a[style*="background: #3498db"]:hover {
        background: #2980b9 !important;
        transform: translateY(-2px);
        box-shadow: 0 4px 15px rgba(52, 152, 219, 0.3);
      }
      
      a[style*="background: #27ae60"]:hover {
        background: #229954 !important;
        transform: translateY(-2px);
        box-shadow: 0 4px 15px rgba(39, 174, 96, 0.3);
      }
      
      /* Responsive design for buttons */
      @media (max-width: 768px) {
        div[style*="display: flex"][style*="gap: 1rem"] {
          flex-direction: column !important;
          align-items: center !important;
        }
        
        div[style*="display: flex"][style*="gap: 1rem"] a {
          width: 200px !important;
          text-align: center !important;
        }
      }
execute:
  echo: false
  warning: false
  message: false
project:
  output-dir: "outputs"
---

```{=html}
<script>
document.addEventListener('DOMContentLoaded', function() {
  // Wait for TOC to be rendered
  setTimeout(function() {
    // Find the sidebar or TOC container
    const sidebar = document.querySelector('.sidebar') ||
                    document.querySelector('#TOC') ||
                    document.querySelector('nav[role="doc-toc"]') ||
                    document.querySelector('.toc-content');
    
    if (sidebar) {
      // Create logo container
      const logoDiv = document.createElement('div');
      logoDiv.style.cssText = `
        text-align: center; 
        padding: 1rem; 
        border-bottom: 1px solid #e0e0e0; 
        margin-bottom: 1rem;
      `;
      
      // Create logo image
      const logoImg = document.createElement('img');
      logoImg.src = 'Relevant_Research_HZ_Color.png';
      logoImg.alt = 'Relevant Research Logo';
      logoImg.style.cssText = `
        height: 80px; 
        max-width: 180px; 
        object-fit: contain;
      `;
      
      // Add error handling for debugging
      logoImg.onerror = function() {
        console.log('Logo failed to load. Check if Relevant_Research_HZ_Color.png exists in project directory.');
        // Create fallback text if image fails
        const fallbackText = document.createElement('div');
        fallbackText.innerHTML = '<strong style="color: #2c3e50;">RELEVANT RESEARCH</strong>';
        fallbackText.style.cssText = `
          height: 80px;
          display: flex;
          align-items: center;
          justify-content: center;
          font-size: 1.2rem;
        `;
        logoDiv.replaceChild(fallbackText, logoImg);
      };
      
      logoImg.onload = function() {
        console.log('Logo loaded successfully!');
      };
      
      logoDiv.appendChild(logoImg);
      
      // Insert at the beginning of sidebar
      sidebar.insertBefore(logoDiv, sidebar.firstChild);
    }
  }, 500);
});
</script>
```
```{r setup, include=FALSE}
library(ggplot2)
library(stringr)
library(dplyr)
library(tidyr)
library(janitor)
library(openxlsx)
library(scales)
library(patchwork)
library(lorem)
library(knitr)
library(DT)
library(leaflet)
```

```{r data-loading, include=TRUE}
# Load interval ADP data - This replaces the Excel-based reported ADP calculations
interval_df <- openxlsx::read.xlsx("IntervalAdpForIndividualColumn_2025-11-28_v1.xlsx",sheet = 1)

# Filter for the specific facility using interval ADP data
facility_interval <- interval_df |>
  filter(Name == str_to_title(params$Name)) |>
  filter(row_number()<2)#|> #Northwest State Correctional in Vermont plus GITMO
  #filter(State == "NY") #Clinton County: NY/IN

detloc <- "LICEPLA"

# Load location data for mapping
fy25_fac_locations <- read.csv("./fy26_detention_output_2025-11-22.csv")
coords <- fy25_fac_locations |>
  filter(Name == params$Name) #|>
  #filter(State == "NY") #Clinton County: NY/IN

# Load facility details from Excel for address and metadata
excel_path <- "FY26_detentionStats12032025.xlsx"
df <- openxlsx::read.xlsx(excel_path, sheet  = "Facilities FY26")

# Get facility metadata from Excel
facility_meta <- df |>
  row_to_names(row_number = 6) |>
  clean_names() |>
  filter(name == params$Name) |>
  filter(row_number()<2)#|> # Prevent duplicates
  #filter(state == "NY") #Clinton County: NY/IN


# Extract location information
City <- facility_meta |> select(c(city))
name <- str_to_title(facility_interval$Name)
Address <- facility_meta |> select(c(address)) |> pull()
State <- facility_meta |> select(c(state)) |> pull()
Zip <- facility_meta |> select(c(zip)) |> pull()
AOR <- facility_meta |> select(c(aor)) |> pull()

# Create dynamic location links
dynamic_address <- paste0(
  str_replace_all(Address, " ", "+"), "+",
  str_replace_all(City, " ", "+"), "+",
  State, "+",
  Zip)


# Create safe dynamic HTML with error handling
safe_dynamic_html <- if(nrow(coords) > 0 && !is.na(params$Longitude) && !is.na(params$Latitude)) {
  paste0('<div style="background: #f8f9fa;
             border-radius: 10px;
             text-align: center;
             margin: 1rem 0;
             border: 1px solid #dee2e6;
            display: flex;
            flex-direction: column;
            justify-content: center;
            align-items: center;
            min-height: 120px;
            padding: 1rem;">
  <div style="display: flex;
               gap: 1rem;
               justify-content: center;
               flex-wrap: wrap;
               margin: 0;">
    <a href="https://maps.google.com/maps?q=', params$Latitude, ',', params$Longitude, '"
       target="_blank"
       style="background: #3498db;
               color: white;
               padding: 0.75rem 1.5rem;
               text-decoration: none;
               border-radius: 5px;
               display: inline-block;
               font-weight: bold;
               transition: all 0.3s ease;">
      🗺️ View Interactive Map
    </a>
    <a href="https://www.google.com/maps/dir//', params$Latitude, ',', params$Longitude, '"
       target="_blank"
       style="background: #27ae60;
               color: white;
               padding: 0.75rem 1.5rem;
               text-decoration: none;
               border-radius: 5px;
               display: inline-block;
               font-weight: bold;
               transition: all 0.3s ease;">
      🧭 Get Directions
    </a>
  </div>
</div>')
} else if(!is.na(Address) && !is.na(City$city) && !is.na(State)) {
  paste0('<div style="background: #f8f9fa;
             border-radius: 10px;
             text-align: center;
             margin: 1rem 0;
             border: 1px solid #dee2e6;
            display: flex;
            flex-direction: column;
            justify-content: center;
            align-items: center;
            min-height: 120px;
            padding: 1rem;">
  <div style="display: flex;
               gap: 1rem;
               justify-content: center;
               flex-wrap: wrap;
               margin: 0;">
    <a href="https://maps.google.com/maps?q=', dynamic_address, '"
       target="_blank"
       style="background: #3498db;
               color: white;
               padding: 0.75rem 1.5rem;
               text-decoration: none;
               border-radius: 5px;
               display: inline-block;
               font-weight: bold;
               transition: all 0.3s ease;">
      🗺️ View Interactive Map
    </a>
    <a href="https://www.google.com/maps/dir//', dynamic_address, '"
       target="_blank"
       style="background: #27ae60;
               color: white;
               padding: 0.75rem 1.5rem;
               text-decoration: none;
               border-radius: 5px;
               display: inline-block;
               font-weight: bold;
               transition: all 0.3s ease;">
      🧭 Get Directions
    </a>
  </div>
</div>')
} else {
  '<div style="background: #f8f9fa; border-radius: 10px; text-align: center; margin: 1rem 0; padding: 1rem;">
    <p style="color: #666;">Location information not available for this facility.</p>
   </div>'
}

# Updated image path to relative
image <- paste0("./interval/", detloc, "_final_plt_2025-12-22.png")
image2 <- paste0("./scatter/", detloc, "_final_2025-12-22.png")
```

::: header-section
# ICE Detention Facility Statistical Report

*Data as of December 11, 2025 - Using Interval ADP Calculations*

[*Back to Detention Reports*](https://detentionreports.com/)
:::

```{r data-preparation, include=FALSE}
# Clean and prepare interval ADP data
facility_clean <- facility_interval |>
  mutate(
    # Use interval ADP columns instead of cumulative
    level_a = round(as.numeric(level_A_back_interval_adp),0),
    level_b = round(as.numeric(level_B_back_interval_adp),0),
    level_c = round(as.numeric(level_C_back_interval_adp),0),
    level_d = round(as.numeric(level_D_back_interval_adp),0),
    male_crim = as.numeric(MaleCrim_back_interval_adp),
    male_non_crim = as.numeric(MaleNonCrim_back_interval_adp),
    female_crim = as.numeric(FemaleCrim_back_interval_adp),
    female_non_crim = as.numeric(FemaleNonCrim_back_interval_adp),
    total_beds = as.numeric(beds_back_interval_adp))
  # ) |>
  # mutate(level_a = ifelse(total_beds < 15, NA, level_a),
  #        level_b = ifelse(total_beds < 15, NA, level_b),
  #        level_c = ifelse(total_beds < 15, NA, level_c),
  #        level_d = ifelse(total_beds < 15, NA, level_d),
  #        male_crim = ifelse(total_beds < 15, NA, male_crim),
  #        male_non_crim = ifelse(total_beds < 15, NA, male_non_crim),
  #        female_crim = ifelse(total_beds < 15, NA, female_crim),
  #        female_non_crim = ifelse(total_beds < 15, NA, female_non_crim))

  # Classification data with proper ordering - using interval ADP
class_data <- facility_clean |>
  select(Name, level_a, level_b, level_c, level_d) |>
  pivot_longer(cols = c(level_a, level_b, level_c, level_d),
               names_to = "Classification",
               values_to = "Population") |>
  mutate(Classification = case_when(
    Classification == "level_a" ~ "Level A",
    Classification == "level_b" ~ "Level B",
    Classification == "level_c" ~ "Level C",
    Classification == "level_d" ~ "Level D"
  )) |>
  filter(Population > 0) |>
  # Add factor ordering to ensure A, B, C, D sequence
  mutate(Classification = factor(Classification, levels = c("Level A", "Level B", "Level C", "Level D")))

# Criminal status data with updated labels - using interval ADP
status_data <- facility_clean |>
  summarise(
    `Male – Criminal` = round(male_crim,0),
    `Male – Non-Criminal` = round(male_non_crim,0),
    `Female – Criminal` = round(female_crim,0),
    `Female – Non-Criminal` = round(female_non_crim,0)
  ) |>
  pivot_longer(everything(),
               names_to = "Category",
               values_to = "Count") |>
  filter(Count > 0)

# Convert necessary columns to numeric and handle missing values
facility_meta_clean <- facility_meta |>
  mutate(
    fy26_alos = as.numeric(fy26_alos),
    guaranteed_minimum = as.numeric(guaranteed_minimum)
  )

# Handle potential missing values
alos_value <- if(is.na(facility_meta_clean$fy26_alos)) {
  "Not Available"
} else {
  paste0(round(facility_meta_clean$fy26_alos, 0), " days")
}

guaranteed_min_value <- if(is.na(facility_meta_clean$guaranteed_minimum)) {
  "Not Available"
} else {
  as.character(facility_meta_clean$guaranteed_minimum)
}

# Summary statistics using interval ADP data
facility_summary <- data.frame(
  Metric = c(
    "Address",
    "Total Average Daily Population (Interval ADP)",
    "Average Length of Stay",
    "Male Population",
    "Female Population", 
    "Criminal Population",
    "Non-Criminal Population",
    "Facility Type",
    "Area of Responsibility",
    "Guaranteed Minimum"
  ),
  Value = c(
    paste0(str_to_title(Address), ", ", str_to_title(City$city), ", ", State, " ", Zip),
    format(round(facility_clean$total_beds, 0), big.mark = ","),
    alos_value,
    format(round(sum(facility_clean$male_crim, facility_clean$male_non_crim, na.rm = TRUE), 0), big.mark = ","), 
    format(round(sum(facility_clean$female_crim, facility_clean$female_non_crim, na.rm = TRUE), 0), big.mark = ","), 
    format(round(sum(facility_clean$male_crim, facility_clean$female_crim, na.rm = TRUE), 0), big.mark = ","), 
    format(round(sum(facility_clean$male_non_crim, facility_clean$female_non_crim, na.rm = TRUE), 0), big.mark = ","),
    ifelse(is.na(facility_meta_clean$type_detailed), "Not Available", str_to_upper(facility_meta_clean$type_detailed)),
    ifelse(is.na(facility_meta_clean$aor), "Not Available", facility_meta_clean$aor),
    guaranteed_min_value
  ))
```

## Key Statistics

```{r summary-table}
kable(facility_summary,
      col.names = c("Facility Metric", "Value"),
      escape = FALSE,
      align = c("l", "r")) |>
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center",
    font_size = 14,
    latex_options = "scale_down"
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::column_spec(2) |>
  kableExtra::row_spec(0, bold = TRUE, background = "#f8f9fa")
```

## Facility Location

::: map-container
```{r facility-map, echo=FALSE, fig.height=4}
# Create interactive map with custom styling
facility_map <- leaflet(width = "100%", height = "400px") %>%
  addTiles() %>%
  setView(lng = params$Longitude, lat = params$Latitude, zoom = 10) %>%
  addMarkers(
    lng = params$Longitude, 
    lat = params$Latitude,
    popup = paste0(
      "<div style='text-align: center; font-family: Arial, sans-serif;'>",
      "<h4 style='margin: 5px 0; color: #2c3e50;'>", facility_meta$name, "</h4>",
      "<p style='margin: 5px 0;'><strong>", Address, "</strong></p>",
      "<p style='margin: 5px 0;'>", City$city, ", ", State, " ", Zip, "</p>",
      "<p style='margin: 5px 0; color: #666;'>", State, "</p>",
      "</div>"
    ),
    label = str_to_title(params$Name)
  )

# Display the map
facility_map
```

```{=html}
`r safe_dynamic_html`
```
<p style="margin-top: 1rem; font-style: italic; color: #666; text-align: center;">

</p>
:::

## Interval Average Daily Population (Interval ADP)

This is a backward moving average calculation of facility populations based on ICE data. For more information, see the background paper [here](https://relevant-research.com/work).

![](`r image`)

## Average Length of Stay and Interval ADP Scatter Plot

![](`r image2`)

::: chart-container
## Interval ADP by Detainee Classification

```{r classification-plot, fig.width=8, fig.height=6}
# Enhanced theme for charts
chart_theme <- theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5, margin = margin(b = 20)),
    plot.subtitle = element_text(size = 12, hjust = 0.5, margin = margin(b = 15)),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 11),
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    plot.margin = margin(15, 15, 15, 15)
  )

# Classification bar chart with ordered x-axis (A, B, C, D)
ggplot(class_data, aes(x = Classification, y = Population, fill = Classification)) +
  geom_col(width = 0.7, alpha = 0.85) +
  geom_text(aes(label = paste0(round(Population, 1))),
            vjust = -0.5,
            size = 4,
            fontface = "bold",
           color = "#2c3e50") +
  scale_y_continuous(
    labels = comma_format(),
    limits = c(0, max(class_data$Population) * 1.15),
    expand = expansion(mult = c(0, 0.05))
  ) +
  scale_fill_manual(values = c("Level A" = "#006475", "Level B" = "#00a1b7", 
                               "Level C" = "#616571", "Level D" = "#9DA7BF")) +
  labs(
    title = "Detainee Classification Distribution",
    subtitle = "Population by Security Level",
    x = "Detainee Classification",
    y = "Average Daily Population"
  ) +
  chart_theme +
  theme(legend.position = "none")
```

ICE defines these classifications as follows:

*Upon admission and periodically thereafter, detainees are categorized into a security level based on a variety of public safety factors, and are housed accordingly.*

*Factors include prior convictions, threat risk, disciplinary record, special vulnerabilities, and special management concerns.*

*Detainees are categorized into one of four classes of security risk:*

-   *A/low*
-   *B/medium low*
-   *C/medium high*
-   *D/high*

\*Due to rounding, summing the Security Classification totals may not equal the facility's aggregate Interval ADP. Please refer to the [notes](https://detentionreports.com/notes.html) page for more information.
:::

## Interval ADP by Gender and Criminal Status

::: chart-container
```{r status-plot, fig.width=8, fig.height=6}
# Status distribution donut chart with smart labeling
# Prepare data with cumulative positions for label placement
status_data_labeled <- status_data %>%
  mutate(
    percentage = Count / sum(Count) * 100,
    # Create labels for all segments
    label_text = paste0(round(percentage, 1), "%\n(", round(Count, 1), ")"),
    # Position labels: large segments inside, small segments in legend with detailed info
    position_type = ifelse(percentage > 10, "inside", "outside")
  )

# Create a more detailed legend that includes the counts
legend_labels <- status_data %>%
  mutate(percentage = Count / sum(Count) * 100) %>%
  arrange(desc(Count)) %>%
  mutate(
    detailed_label = paste0(Category, ": ", round(percentage, 1), "% (", round(Count, 1), ")")
  ) %>%
  pull(detailed_label)

# Create the plot
p <- ggplot(status_data, aes(x = 2, y = Count, fill = Category)) +
  geom_bar(stat = "identity", width = 1, alpha = 0.85) +
  coord_polar("y", start = 0) +
  scale_fill_manual(
    values = c("Female – Criminal" = "#006475", 
               "Female – Non-Criminal" = "#00a1b7", 
               "Male – Criminal" = "#616571", 
               "Male – Non-Criminal" = "#9DA7BF"),
    labels = function(x) {
      # Create detailed labels for legend
      sapply(x, function(cat) {
        row_data <- status_data[status_data$Category == cat, ]
        if(nrow(row_data) > 0) {
          pct <- round(row_data$Count / sum(status_data$Count) * 100, 1)
          paste0(cat, ": ", pct, "% (", round(row_data$Count, 1), ")")
        } else {
          cat
        }
      })
    }
  ) +
  # Only label the largest segment to avoid collision
  geom_text(
    data = status_data %>%
            mutate(percentage = Count / sum(Count) * 100) %>%
           filter(percentage > 10),
    aes(label = paste0(round(Count/sum(status_data$Count)*100, 1), "%\n(", round(Count, 1), ")")),
    position = position_stack(vjust = 0.5),
    size = 3.5,
    fontface = "bold",
    color = "white"
  ) +
  xlim(0.5, 2.5) +
  labs(
    title = "Population by Gender and Criminal Status",
    subtitle = "Percentage (Approximate Pop.)"
  ) +
  chart_theme +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.margin = margin(t = 15),
    legend.box.margin = margin(t = 10),
    legend.text = element_text(size = 10)
  ) +
  guides(fill = guide_legend(ncol = 2))

p
```

ICE defines criminality as follows:

-   *Convicted Criminal:*
    -   *Immigration Violators with a criminal conviction entered into ICE systems of record at the time of ICE custody.*\
-   *Pending Criminal Charges:*
    -   *Immigration Violators with pending criminal charges entered into ICE system of record at the time of ICE custody.*\
-   *Other Immigration Violators:*
    -   *Immigration Violators without any known or a criminal conviction, or pending charges entered into ICE system of record at the time of ICE custody.*

ICE reduces these three categories into two for their facility reporting: "Criminal" and "Non-Criminal". ICE does not clearly explain its method for disaggregating criminality in ICE Detention Statistics documentation. Comparing percentages across other ICE reporting metrics suggests that ICE includes people with Pending Criminal Charges as part of the "Non-Criminal" category for reporting purposes.

\*Due to rounding, summing the Gender and Criminal Status totals may not equal the facility's aggregate Interval ADP. Please refer to the [notes](https://detentionreports.com/notes.html) page for more information.
:::

[*Back to Detention Reports*](https://detentionreports.com/)

------------------------------------------------------------------------

::: {style="text-align: center; color: #666; font-size: 0.9em; margin-top: 3rem;"}
<em>Report generated on `r format(Sys.Date(), "%B %d, %Y")` using ICE Integrated Decision Support (IIDS) interval ADP data from December 11, 2025</em>

Developed by [Relevant Research](https://relevant-research.com/). For information about the methodology behind Interval ADP, [click here](https://relevant-research.com/work).
:::
